Value Ordering, Discrepancies, and Restarts for Subgraph Isomorphism

### 2017-12-07 paper/paper.tex
More
Tweak for no reason

\title{Value Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking
Around}
\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/026842/1]}\\ University of Glasgow, Glasgow, Scotland \\
    ciaran.mccreesh@glasgow.ac.uk}

@@

\begin{abstract}
    Modern subgraph isomorphism solvers use value-ordering heuristics to direct search, but these
    heuristics are not perfect, particularly for early choices. We investigate discrepancy searches
    and restarts to offset this weakness. Our results suggest that discrepancy-based searches are
    too expensive to be effective.  However, restarts with a random value-ordering heuristic beats
    conventional search with the best tailored heuristic. This motivates the introduction of a
    slightly-random value-ordering heuristic with similar behaviour to the tailored heuristic: when
    combined with restarts, this new heuristic is even more effective on satisfiable instances,
    whilst not significantly decreasing performance on unsatisfiable instances.
\end{abstract}

@@

The current single strongest subgraph isomorphism solver uses ``highest degree first'' as a
value-ordering heuristic \citep{dblp:conf/cp/McCreeshP15,dblp:conf/ijcai/McCreeshPT16}.  This is
much better than not having a value-ordering heuristic at all, but it is far from perfect,
particularly for early branching choices. There are two reasons to suspect we could do better.
Firstly, even if degree were a perfect source of information, many graphs do not have a large degree
distribution, and so we would still need to determine \emph{which} vertex of highest degree would be
best.  Secondly, experiments with a parallel search strategy which explicitly steals early branching
choices often gives strongly super-linear speedups on satisfiable instances
\citep{dblp:conf/cp/McCreeshP15}.

@@

?? Other studies use a random selection of 200 of each of the mesh and images instances
\citep{DBLP:journals/cviu/DamiandSHJS11}, partly because some earlier solvers find many of these
instances extremely hard, and partly to avoid skewing a portfolio. We want larger numbers of
satisfiable instances, so we include all pattern / target pairs. This gives a total of 14,621
instances, at least 2,110 of which are known to be satisfiable, and at least 12,323 are
unsatisfiable.

@@

>>>>

\title{Value Ordering, Discrepancies, and Restarts for Subgraph Isomorphism}
\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/026842/1]}\\ University of Glasgow, Glasgow, Scotland \\
    ciaran.mccreesh@glasgow.ac.uk}

@@

\begin{abstract}
    Modern subgraph isomorphism solvers use value-ordering heuristics to direct a constraint
    programming style search. These heuristics are not perfect, particularly for early branching
    choices. We show that discrepancy-based searches are too expensive to be effective in this
    setting.  However, using restarts with a random value-ordering heuristic beats conventional
    search with the best tailored heuristic.  This motivates the introduction of a slightly-random
    value-ordering heuristic with similar behaviour to the tailored heuristic: when combined with
    restarts, this new search strategy is even more effective on satisfiable instances, whilst not
    significantly decreasing performance on unsatisfiable instances.
\end{abstract}

@@

The current single strongest subgraph isomorphism solver uses ``highest degree first'' as a
value-ordering heuristic \citep{dblp:conf/cp/McCreeshP15,dblp:conf/ijcai/McCreeshPT16}.  This is
much better than not having a value-ordering heuristic at all, but it is far from perfect,
particularly for early branching choices. There are two reasons to suspect a better option may
possible.  Firstly, even if degree were a perfect source of information, many graphs do not have a
large degree distribution, and so we would still need to determine \emph{which} vertex of highest
degree would be best.  Secondly, experiments with a parallel search strategy which explicitly steals
early branching choices often gives strongly super-linear speedups on satisfiable instances
\citep{dblp:conf/cp/McCreeshP15}.

@@

?? Other studies use a random selection of 200 of each of the mesh and images instances
\citep{DBLP:journals/cviu/DamiandSHJS11}, partly because some earlier solvers find many of these
instances extremely hard, and partly to avoid skewing a portfolio. We want larger numbers of
satisfiable instances, so we include all pattern / target pairs. This gives a total of 14,621
instances, at least 2,126 of which are known to be satisfiable, and at least 12,323 are
unsatisfiable.

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-parallel.pdf}

    \caption{Parallel}
    \label{figure:scatter-parallel}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-final.pdf}

    \caption{Final results}
    \label{figure:final}
\end{figure}
